---
title: "simpleRegress"
author: Mya Orozco
date: Fall 2024
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model WEIGHT ~ NECK  this is an example  

```{r}
simp <- lm(WEIGHT~NECK,data=bears)
plot(WEIGHT~NECK,data=bears)
abline(simp)
summary.lm(simp)
```


## Compare all models that predict WEIGHT other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

## Model WEIGHT ~ AGE  this is an example  
 
```{r}
agemodel <- lm(WEIGHT~AGE,data=bears)
plot(WEIGHT~AGE,data=bears)
abline(agemodel)
summary.lm(agemodel)
```

1. Neck-->  ARsqrd: 0.87,  RST:43.91  
2. Age-->    ARsqrd: 0.55,  RST:81.47  
The agemodel graph shows its points to be far away from the line, while the simp graph has plots closer to it.

```{r}
headlemodel <- lm(WEIGHT~HEADLEN,data=bears)
plot(WEIGHT~HEADLEN,data=bears)
abline(headlemodel)
summary.lm(headlemodel)
```

Worst to best  
1. Age        -->   ARsrd: 0.55,        RST:81.47  
2. Head length-->    ARsqrd:0.69,        RST:67.81  
3. Neck       -->       ARsqrd:0.87,       RST:43.91  

Comparing the Adjusted R-squared being higher at 0.69 and the agemodel Adjusted R-squared is 0.55, shows it being better than it but not high enough for simps Adjusted r-squared of 0.87.


```{r}
headwthmodel <- lm(WEIGHT~HEADWTH,data=bears)
plot(WEIGHT~HEADWTH,data=bears)
abline(headwthmodel)
summary.lm(headwthmodel)
```

Worst to best  
1. Age        -->       ARsrd: 0.55        RST:81.47   
2. Head width -->       ARsqrd:0.60        RST:76.41  
3. Head length-->       ARsqrd:0.69        RST:67.81  
4. Neck       -->       ARsqrd:0.87        RST:43.91  

headwthmodel would have a high Residual standard error of 76.41, being lower than agemodel's 81.47 but not enough for headlenmodel's 67.81 Residual standard error.






